---
title: "team"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#1
choco <-
  read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
head(choco)

recent_rating = choco[choco$Review.Date > 2011, ]
# create a dataframe called recent_rating which is part of dataframe choco. It is contained reveiw data after 2011 from dataset choco.

unique(recent_rating$Company.Location)
# listed all contries existed in the recent_rating dataframe without repeated by appearing sequence. Level 61 means there are 61 different countries, however, some of them are not existed.

recent_rating$Company.Location = droplevels(recent_rating$Company.Location)
# it is used to drop unusual levels from Company.Location in dataframe recent_rating

head(recent_rating)
# get the several top data of the dataset recent_rating.

cross_table = table(recent_rating$Review.Date, recent_rating$Company.Location)
cross_table
#create a table to show different Company.Location by the Review.Date(2012,2013,2014,2015,2016,2017))

which(
  cross_table[1, ] != 0 &
    cross_table[2, ] != 0 &
    cross_table[3, ] != 0 & cross_table[4, ] != 0 & cross_table[5, ] != 0
)
# choose several sepcific data which satisfied all years did have zero data in a certain country.

france_recent = subset(recent_rating, Company.Location == 'France')
uk_recent = subset(recent_rating, Company.Location == 'U.K.')
germany_recent = subset(recent_rating, Company.Location == 'Germany')
#create a subdataframe called france_recent which contains all the data whose Company.Location is France.
#create a subdataframe called uk_recent which contains all the data whose Company.Location is UK.
#create a subdataframe called germany_recent which contains all the data whose Company.Location is Germany.
#2
use different pch vaule such as pch =2, pch =10
the different plot of the graph could make people see more clearly 
#3.
```{r}
choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
Rating_Year <- table(choco$Rating, choco$Review.Date)
barplot(colSums(Rating_Year))
```




#4  
```{r}
Q4 <- table(choco$Rating, choco$Company.Location)
Q4_table1 <- colSums(Q4)
sort(Q4_table1, decreasing = TRUE)
com1 <- cbind(Q4[, "U.S.A."], Q4[, "France"], Q4[, "Canada"])
com1
Q4_table2 <- data.frame(com1)
Q4_table2
com2 <- sort(unique(choco$Rating), decreasing = FALSE)
par(mfrow = c(2, 2))
plot(
  com2,
  Q4_table2$X1,
  pch = 10,
  col = 'blue',
  xlim = c(1, 5),
  xlab = "rating",
  ylab = 'USA'
)
plot(
  com2,
  Q4_table2$X2,
  pch = 2,
  col = 'red',
  xlab = "rating",
  ylab = 'France'
)
plot(
  com2,
  Q4_table2$X3,
  pch = 18,
  col = 'purple',
  xlab = "rating",
  ylab = 'Canada'
)
```
#5 which counrty has the most high rating and lowest rating 
